We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-02-07 paper/paper.tex
sigma outlier
edit

The fits to the multivariate gaussian distributions can be used now to
compute the expected number of pairs with characteristics similar to
the LG.
To do this we generate $10^3$ samples, each sample contains $10^4$
pairs, where each pair member is drawn from the corresponding
multivariate gaussian distributions.

@@

We consider that a sampled system is similar to the M31/MW galaxy if the
distance of each of its characteristics ($w$, $c/a$, $b/a$) to the
sample mean is larger than the distance of the observational values to
the sample mean. 
That is, we perform a double-tailed test using the observational
values as a threshold.

Under this conditions

>>>>

We us the fits to the multivariate gaussian distributions to
compute the expected number of pairs with characteristics similar to
the LG.
To do this we generate $10^3$ samples, each sample contains $10^4$
pairs, where each pair member is drawn from the corresponding
multivariate gaussian distributions.

We consider that a sampled system is similar to the M31/MW galaxy if the
distance of each of its characteristics ($w$, $c/a$, $b/a$) to the
sample mean is equal or larger than the distance of the observational
values to the sample mean.   
That is, we perform a double-tailed test using the observational
values as a threshold.

@@

In a three dimensional gaussian distribution, having a $1\sigma$,
$2\sigma$ and $3\sigma$ interval corresponds to have respectively $19 \%$, $73 \%$ and
$97 \%$ of the total of points in the distribution.
% FUNDAMENTALS OF MULTIVARIATE STATISTICS, for Imaging and optics,
% Bajorski.
%In [150]: stats.chi2.cdf(l**2,3)
%Out[150]: array([ 0.19874804,  0.73853587,  0.97070911])
With this consideration, the $LG$ has the same degree of atipicality
as an $3\sigma$ outlier.
